Peptide retention time prediction

### 2015-01-25 retention.tex
Added overview image

\begin{wrapfigure}{r}{.45\textwidth}
\vspace{-10pt}
%\begin{figure}[htbp]
\centering
\includegraphics[trim=0.5cm 0cm 2cm 1.5cm, clip=true, width=0.43\textwidth]{img/reproducibility.pdf}
\caption{\label{fig:repr} {\bf Reproducibility of peptide retention time.} Two identical shotgun proteomics experiments were carried out. The retention times of the peptides confidently identified in both runs are displayed.}
%\end{figure}
\vspace{-25pt}
\end{wrapfigure}

% iRT? \cite{Escher:2012qv}
Following these observations, a variety of retention time prediction
methods has been proposed. Most naturally one could divide these
methods into four classes: look-up tables-based approaches,
index-based methods, modeling-based methods and machine learning
techniques. The main ideas underlying each category are described
below, while Table \ref{tab:rtmethods} lists a few of the most popular
retention time prediction methods from each category.

>>>>

\begin{wrapfigure}{r}{.45\textwidth}
\vspace{-10pt}
%\begin{figure}[htbp]
\centering
\includegraphics[trim=0.5cm 0cm 2cm 1.5cm, clip=true, width=0.43\textwidth]{img/reproducibility.pdf}
\caption{\label{fig:repr} {\bf Reproducibility of peptide retention
    time.} Two identical shotgun proteomics experiments were carried
  out. The retention times of the peptides confidently identified in
  both runs are displayed.}
%\end{figure}
\vspace{-60pt}
\end{wrapfigure}

% iRT? \cite{Escher:2012qv}
Following these observations, a variety of retention time prediction
methods has been proposed. Most naturally one could divide these
methods into four classes: look-up tables-based approaches,
index-based methods, modeling-based methods and machine learning
techniques. The main ideas underlying each category are illustrated in
\ref{fig:methods} , while Table \ref{tab:rtmethods} lists a few of the
most popular retention time prediction methods from each category.

\begin{figure}[!h]
\centering \includegraphics[clip=true,
  width=0.8\textwidth]{img/methods.pdf}
\caption{\label{fig:methods} {\bf Retention time prediction methods.}
  Each figure illustrates a category of retention time prediction
  methods. The details of each type of methods are described in detail
  in Section \ref{sec:rtpred}}.
\vspace{-7pt}
\end{figure}
